### 2018-03-26 reports/thesis/chapters/5_inference.tex
Completed multiple hypothesis section.

Bringing in methods from single hypothesis testing to the multiple version has drawbacks. Assuming that the null hypothesis is true for all $Z_i$ for $i=1,2,\dotdotdot,n$, then by definition $\alpha\approx 4.55\%$ of the data will be tested positive, and falsely positive. Still under the same assumption, the probability of at least one positive result, known as the family-wise error rate (FWER) \citep{shaffer1995multiple}, is
\begin{align}
    \text{FWER}&=1-\prob(\text{no false positives}) \nonumber\\
    \text{FWER}&=1-\prob(\text{no positive results}|H_0) \nonumber\\
    \text{FWER}&=1-\left[(1-\alpha)^n\right] \label{eq:inference_fwer}\ .
\end{align}
To put into context, for $\alpha\approx 4.55\%$ and $n=20$ then remarkably $\text{FWER}\approx60.6\%$. This method for multiple hypothesis testing will have too many false positive results.

@@

The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the false positive or family-wise rate. The FDR is the proportion of false positives out of all positive results, that is
\begin{equation}
    \expectation[\text{FDR}] = \expectation\left[
        \dfrac{V}{R}
    \right]
    \ .
\end{equation}
It is defined that $\text{FDR}=0$ when $R=0$.

@@

The ordered $p$-values are shown in Figure \ref{fig:altpvalues}. This time there are $p$-values below the critical line according to the BH procedure, testing $\input{../figures/inference/alt_n_positive_bh.txt}$ test statistics as positive. The uncorrected test tested $\input{../figures/inference/alt_n_positive_uncorrected.txt}$ test statistics as positive.

@@

\begin{table}
    \centering
    \input{../tables/inference_error_rate1.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, all standard Normal. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
\end{table}

\begin{table}
    \centering
    \input{../tables/inference_error_rate2.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, 800 from the standard Normal, 200 from $\normal(2,1)$. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
\end{table}

>>>>

Bringing in methods from single hypothesis testing to the multiple version has drawbacks. Assuming that the null hypothesis is true for all $Z_i$ for $i=1,2,\dotdotdot,n$, then by definition $\alpha\approx 4.55\%$ of the data will be tested positive, and falsely positive. Still under the same assumption, the probability of at least one false positive result, known as the family-wise error rate (FWER) \citep{shaffer1995multiple}, is
\begin{align}
    \text{FWER}&=1-\prob(\text{no false positives}) \nonumber\\
    \text{FWER}&=1-\prob(\text{no positive results}|H_0) \nonumber\\
    \text{FWER}&=1-\left[(1-\alpha)^n\right] \label{eq:inference_fwer}\ .
\end{align}
To put into context, for $\alpha\approx 4.55\%$ and $n=20$ then remarkably $\text{FWER}\approx60.6\%$. This method for multiple hypothesis testing will have too many false positive results.

@@

The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the false positive or family-wise rate. The FDR is the proportion of false positives out of all positive results, that is
\begin{equation}
    \text{FDR} = \expectation\left[
        \dfrac{V}{R}
    \right]
    \ .
\end{equation}
It is defined that $V/R=0$ when $R=0$.

@@

The ordered $p$-values are shown in Figure \ref{fig:altpvalues}. There are $p$-values below the critical line according to the BH procedure, testing $\input{../figures/inference/alt_n_positive_bh.txt}$ test statistics as positive. The uncorrected test tested $\input{../figures/inference/alt_n_positive_uncorrected.txt}$ test statistics as positive.

@@

The error rates can be estimated as a result of knowing whenever each test statistic is truly null or non-null. Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ test statistics were tested positive. From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed, following the notation in Table \ref{table:inference_randomvariables}. The error rates can be estimated
\begin{equation}
	\widehat{\text{PCER}} = \frac{1}{Nn}\sum_{i=1}^N v_i
\end{equation}
\begin{equation}
	\widehat{\text{FWER}} = \frac{1}{N} \sum_{i=1}^N \mathbb{I}(v_i\neq 0)
\end{equation}
\begin{equation}
	\widehat{\text{FDR}} = \frac{1}{N}\sum_{i=1}^N\dfrac{v_i}{r_i}\times\mathbb{I}(r_i\neq0)
	\ .
\end{equation}
The estimates of PCER and FDR is esentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the variance of the Beta distribution is used to quantify the error
\begin{equation}
	\text{standard error of }\widehat{\text{FWER}} = 
	\sqrt{\dfrac{ab}{(a+b)^2(a+b+1)}}
\end{equation}
where $a = \sum_{i=1}^N \mathbb{I}(v_i\neq 0)$ and $b = N - a$.

\begin{table}
    \centering
    \input{../tables/inference_error_rate1.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, all standard Normal. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
    \label{table:inference_error_rate1}
\end{table}

\begin{table}
    \centering
    \input{../tables/inference_error_rate2.tex_table}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, 800 from the standard Normal, 200 from $\normal(2,1)$. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
     \label{table:inference_error_rate1}
\end{table}

Error rates estimations for the two scenarios are shown in Tables \ref{table:inference_error_rate1} and \ref{table:inference_error_rate1} for $N=1\,000$. These estimations show that the 3 different types of multiple hypothesis controls for different rates. The uncorrected, Bonferroni and BH controls the PCER, FWER and FDR to be equal or below $\alpha\approx 0.455$ respectively, equality is met when all the test statistics are all truly null.
